Figures to insert in text

### 2018-04-04 kanerva-answer.tex
SDM Answer to Kanerva

\begin{align}
Y_i = \sum_{k=1}^{\theta} X_k \sim \mathcal{N}(\mu_1 = p \theta, \sigma_1^2 = p(1-p) \theta + p^2 s^2 p_1 (1 - p_1) / H)
\end{align}

>>>>

\begin{align}
Y_i = \sum_{k=1}^{\theta} X_k \sim \mathcal{N}(\mu_1, \sigma_1^2)
\end{align}

Applying the law of total expectation, $\mathbf{E}[Y] = \mathbf{E}[\mathbf{E}[Y|\theta]] = \mathbf{E}[p \theta] = p \mathbf{E}[\theta] = p \theta$, since $\mathbf{E}[\theta] = \theta$.

Applying the law of total variance, $\mathbf{V}[Y] = \mathbf{E}[\mathbf{V}[Y|\theta]] + \mathbf{V}[\mathbf{E}[Y|\theta]] = \mathbf{E}[\theta p (1-p)] + \mathbf{V}[p \theta] = p(1-p) \mathbf{E}[\theta] + p^2 \mathbf{V}[\theta] = p(1-p) \theta + p^2 s^2 p_1 (1-p_1)/H$, since $\mathbf{V}[\theta] = s^2 p_1 (1-p_1)/H$.

Thus,

\begin{align}
\mu_1 &= p \theta \\
\sigma_1^2 &= p^2 s^2 p_1 (1 - p_1) / H
\end{align}
